---
title: "ESM: MCMC diagnostics and detailed estimations"
output: rmarkdown::html_document
params:
  end_date: "2020-09-16"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  class.warning = "collapsable-warnings",
  message = FALSE
)
```

```{r}
library(dplyr)
library(coda)
```

```{r}
library(NpiEurope)
npi_europe <- load_npi_data(end_date = params$end_date)
```

```{r}
nchains <- length(readRDS("../MCMC_NpiEurope/Austria.rds")$samples)
```

We estimated transmission rates per country over time through Bayesian inference
by running a particle Monte Carlo Markov Chain (pMCMC) with the epidemiological
model described earlier. Each of the `r nchains` chains had 2,500 iterations
with a thinning of 1/10. The likelihood was computed with a particle filter of
50 particles and a negative binomial function of parameter 0.5 on the total
daily number of new cases expected by the model and observed in the data (i.e.,
number of cases notified to the national public health system and number of
undetected cases estimated by the capture/recapture method). The ratio between
transmission rates with and without implementation of the PHR evaluated provides
an estimation of the efficiency of this response, therefore assuming that it had
an instantaneous effect.

```{r, results='asis'}
tabres <- list.files("../MCMC_NpiEurope/", "\\.rds$", full.names = TRUE) %>%
  lapply(function(f) {
    
      country <- gsub(".*/((\\w|\\s)+)\\.rds$", "\\1", f)
      
      message(country)

      npi_country <- npi_europe %>%
        filter(Country == country) %>%
        select(-Country)
      
      mcmcout <- readRDS(f)
      
      cat("### ", country, "\n\n")
      
      plot(mcmcout$samples[, "transmRate", drop = FALSE])
      
      for (i in 2:ncol(mcmcout$samples[[1]])) {
        par(mfrow = c(1, 2))
        coda::traceplot(mcmcout$samples[, i, drop = FALSE], ylim = c(0, 1))
        coda::densplot(mcmcout$samples[, i, drop = FALSE], xlim = c(0, 1))
      }
      

      res <- summarise_estimation(mcmcout, npi_country)
     
      # This is not an issue since the computation of effectiveSize is affine-invariant 
      mcmcout <- coda::as.mcmc.list(
        lapply(mcmcout$samples, function(m) {
          m[, "transmRate"] <- m[, "transmRate"] * 1e8
          return(m)
        })
      )
      
      res$ESS <- coda::effectiveSize(mcmcout$samples)
      
      # res$Geweke <- sprintf("%.2e", pnorm(abs(geweke.diag(mcmcout)$z),lower.tail=FALSE)*2)
      
      print(knitr::kable(
        res, 
        digits = 2,
        caption = paste0(
          "Efficiencies of the PHR implemented in ", country, ". The first ",
          "column contains the list of the NPIs in the current PHR, the second",
          " and third columns contain the 95% credibility interval of the ",
          "estimation. The fourth and fifth column contain the day of start ",
          "and end of the current PHR and the last column contains the ",
          "effective sample size of the MCMC estimation."
        )
      ))

  })
```

```{r, child='_sessionInfo.Rmd'}
```

```{js, echo=FALSE}
(function() {
  var codes = document.querySelectorAll('.collapsable-warnings');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Warnings';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
})();
```

