---
title: "ESM: MCMC diagnostics and detailed estimations"
output: rmarkdown::html_document
params:
  end_date: "2020-09-16"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  class.warning = "collapsable-warnings",
  message = FALSE
)
```

```{r}
library(dplyr)
```

```{r}
library(NpiEurope)
npi_europe <- load_npi_data(end_date = params$end_date)
```

We estimated transmission rates per country over time through Bayesian inference
by running a particle Monte Carlo Markov Chain (pMCMC) with the epidemiological
model described earlier. The chains had 10,000 iterations with a thinning of
1/10. The likelihood was computed with a particle filter of 20 particles and a
negative binomial function of parameter 0.5 on the total daily number of new
cases expected by the model and observed in the data (i.e., number of cases
notified to the national public health system and number of undetected cases
estimated by the capture/recapture method). The ratio between transmission rates
with and without implementation of the PHR evaluated provides an estimation of
the efficiency of this response, therefore assuming that it had an instantaneous
effect.

```{r, results='asis'}
tabres <- list.files("../1stwave_goodstart/", "\\.csv$", full.names = TRUE) %>%
  lapply(function(f) {
    
      country <- gsub(".*/((\\w|\\s)+)\\.csv$", "\\1", f)
      
      message(country)

      npi_country <- npi_europe %>%
        filter(Country == country) %>%
        select(-Country)
    
      contact_country <- load_contact_data(country)
      age_country <- sirage::load_age_data(country)
      
      mcmcout1 <- read.csv(sprintf("../%s/%s.csv", "MCMC_NpiEurope_1stwave_2020-12-19", country)) %>%
#        filter(Iteration > 500) %>%
        select(-Iteration, -Likelihood) %>%
        mutate(R0 = sirage::transmRate_to_R0(transmRate, age_country, contact_country),
               .keep = "unused",
               .before = 1) %>%
        coda::as.mcmc(start = 1, thin = 10)
      mcmcout2 <- read.csv(sprintf("../%s/%s.csv", "MCMC_NpiEurope_1stwave_2020-12-19_2", country)) %>%
#        filter(Iteration > 500) %>%
        select(-Iteration, -Likelihood) %>%
        mutate(R0 = sirage::transmRate_to_R0(transmRate, age_country, contact_country),
               .keep = "unused",
               .before = 1) %>%
        coda::as.mcmc(start = 1, thin = 10)
      # mcmcout3 <- read.csv(sprintf("../%s/%s.csv", "MCMC_NpiEurope_1stwave_2020-12-19_3", country)) %>%
      #   select(-Iteration, -Likelihood) %>%
      #   coda::as.mcmc()
      mcmcout <- coda::mcmc.list(mcmcout1, mcmcout2)
      
      cat("### ", country, "\n\n")
      
      plot(mcmcout[, "R0", drop = FALSE])
      
      for (i in 2:ncol(mcmcout[[1]])) {
        par(mfrow = c(1, 2))
        coda::traceplot(mcmcout[, i, drop = FALSE], ylim = c(0, 1))
        coda::densplot(mcmcout[, i, drop = FALSE], xlim = c(0, 1))
      }
      
      # This is not an issue since the computation of effectiveSize is affine-invariant
      res <- summarise_estimation(mcmcout, npi_country)
      
      res$ESS <- coda::effectiveSize(mcmcout)
      
      # res$Geweke <- sprintf("%.2e", pnorm(abs(geweke.diag(mcmcout)$z),lower.tail=FALSE)*2)
      
      print(knitr::kable(
        res, 
        digits = 2,
        caption = paste0(
          "Efficiencies of the PHR implemented in ", country, ". The first ",
          "column contains the list of the NPIs in the current PHR, the second",
          " and third columns contain the 95% credibility interval of the ",
          "estimation. The fourth and fifth column contain the day of start ",
          "and end of the current PHR and the last column contains the ",
          "effective sample size of the MCMC estimation."
        )
      ))

  })
```

```{r, child='_sessionInfo.Rmd'}
```

```{js, echo=FALSE}
(function() {
  var codes = document.querySelectorAll('.collapsable-warnings');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Warnings';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
})();
```

